---
title: "Subset Selection"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(readr)
library(broom)
library(ggplot2)
library(tidymodels) 
tidymodels_prefer() # Resolves conflicts, prefers tidymodel functions
```

## Read in Data

```{r}
homes <- read_tsv("http://sites.williams.edu/rdeveaux/files/2014/09/Saratoga.txt")

head(homes)

# Creating Factors - permanent change in data
homes <- homes %>%
  mutate(
      Fuel.Type = factor(Fuel.Type, levels = 2:4, labels=c('gas','electric','oil')),
      Heat.Type = factor(Heat.Type, levels = 2:4, labels=c('hot air','hot water/steam','electric')),
      Sewer.Type = factor(Sewer.Type, levels = 1:3, labels = c('none','septic','public/commercial')),
      AnyFireplace = if_else(Fireplaces > 0, 1,0))
```

## Model  Specification & Fold Creation

```{r}
lm_spec <- 
    linear_reg() %>% # this is the type of model we are fitting
    set_engine(engine = 'lm') %>% # you'll learn other engines to fit the model
    set_mode('regression') # we'll talk about other modes such as classification later

set.seed(123)
homes_cv10 <- vfold_cv(homes, v = 10)
```

## Forward Selection

See R Code below to manually code, but forward selection is not a recommended practice for variable/feature selection.

### One Variable Models

```{r}
vars <- names(homes)
vars <- vars[vars != 'Price']

formulas <- map(paste0('Price ~ ',vars), ~ formula(.x)) # create list of 1 variable formulas
names(formulas) <- vars

homes_1varmodels <- workflow_set(preproc = formulas, models = list(lm = lm_spec))

homes_1varmodels_fit <- homes_1varmodels %>%
  workflow_map("fit_resamples", resamples = homes_cv10,  metrics = metric_set(rmse, rsq))

homes_1varmodels_fit %>% 
   rank_results() %>% 
   filter(.metric == "rmse") %>% 
   select(wflow_id, .config, rmse = mean, rank)
```

### Two Variable Models

Choose second variable to complement best first variable

```{r}
vars <- vars[!(vars %in% c('Price','Living.Area'))]
formulas <- map(paste0('Price ~ Living.Area + ',vars), ~ formula(.x)) #create list of 2 variable formulas
names(formulas) <- paste0('Living.Area_',vars)

homes_2varmodels <- workflow_set(preproc = formulas,models = list(lm = lm_spec))

homes_2varmodels_fit <- homes_2varmodels %>%
  workflow_map("fit_resamples", resamples = homes_cv10,  metrics = metric_set(rmse,rsq))

homes_2varmodels_fit %>% 
   rank_results() %>% 
   filter(.metric == "rmse") %>% 
   select(wflow_id, .config, rmse = mean, rank)
```

### Three Variable Models

Choose third variable to complement best two variables

```{r}
vars <- vars[!(vars %in% c('Price','Living.Area','Land.Value'))]
formulas <- map(paste0('Price ~ Living.Area + Land.Value + ',vars), ~formula(.x)) #create list of 3 variable formulas
names(formulas) <- paste0('Living.Area_Land.Value_',vars)

homes_3varmodels <- workflow_set(preproc = formulas, models = list(lm = lm_spec))

homes_3varmodels_fit <- homes_3varmodels %>%
  workflow_map("fit_resamples", resamples = homes_cv10,  metrics = metric_set(rmse,rsq))

homes_3varmodels_fit %>% 
   rank_results() %>% 
   filter(.metric == "rmse") %>% 
   select(wflow_id, .config, rmse = mean, rank)
```

### Four Variable Models

Choose fourth variable to complement best three variables

```{r}
vars <- vars[!(vars %in% c('Price','Living.Area','Land.Value','Bathrooms'))]
formulas <- map(paste0('Price ~ Living.Area + Land.Value + Bathrooms +',vars), ~ formula(.x)) #create list of 4 variable formulas
names(formulas) <- paste0('Living.Area_Land.Value_Bathrooms_',vars)

homes_4varmodels <- workflow_set(preproc = formulas,models = list(lm = lm_spec))

homes_4varmodels_fit <- homes_4varmodels %>%
  workflow_map("fit_resamples", resamples = homes_cv10,  metrics = metric_set(rmse,rsq))

homes_4varmodels_fit %>% 
   rank_results() %>% 
   filter(.metric == "rmse") %>% 
   select(wflow_id, .config, rmse = mean, rank)
```

Continue on...


## Backward Selection

See R Code below to manually code, but backward selection is not a recommended practice for variable/feature selection.

### Full Model

```{r}
vars <- names(homes)
vars <- vars[vars != 'Price']
formulas <- list(formula(paste0('Price ~ ', paste0(vars, collapse = '+'))))
names(formulas) <- 'full'

homes_fullvarmodels <- workflow_set(preproc = formulas, models = list(lm = lm_spec))

homes_fullvarmodels_fit <- homes_fullvarmodels %>%
  workflow_map("fit_resamples", resamples = homes_cv10,  metrics = metric_set(rmse,rsq))

homes_fullvarmodels_fit %>% 
   rank_results() %>% 
   filter(.metric == "rmse") %>% 
   select(wflow_id, .config, rmse = mean, rank)
```

### Remove 1 from Model

```{r}
vars <- vars[vars != 'Price']

formulas <- map(vars, ~ formula(paste0('Price ~ ',paste0(vars[vars != .x], collapse = '+'))))
names(formulas) <- paste0('full-',vars)

homes_rm1varmodels <- workflow_set(preproc = formulas,models = list(lm = lm_spec))

homes_rm1varmodels_fit <- homes_rm1varmodels %>%
  workflow_map("fit_resamples", resamples = homes_cv10,  metrics = metric_set(rmse,rsq))

homes_rm1varmodels_fit %>% 
   rank_results() %>% 
   filter(.metric == "rmse") %>% 
   select(wflow_id, .config, rmse = mean, rank) 
```
Removing Sewer Type gives the lowest error, meaning that removing it does the least harm to the predictive ability of the model. 

### Remove 2 from Model


```{r}
vars <- vars[!(vars %in% c('Price','Sewer.Type'))]

formulas <- map(vars, ~formula(paste0('Price ~ ',paste0(vars[vars != .x], collapse = '+'))))
names(formulas) <- paste0('full-Sewer.Type-',vars)

homes_rm2varmodels <- workflow_set(preproc = formulas, models = list(lm = lm_spec))

homes_rm2varmodels_fit <- homes_rm2varmodels %>%
  workflow_map("fit_resamples", resamples = homes_cv10,  metrics = metric_set(rmse,rsq))

homes_rm2varmodels_fit %>% 
   rank_results() %>% 
   filter(.metric == "rmse") %>% 
   select(wflow_id, .config, rmse = mean, rank)
```

Removing Fuel.Type gives the lowest error, meaning that removing it does the least harm to the predictive ability of the model. 


### Remove 3 from Model


```{r}
vars <- vars[!(vars %in% c('Price','Sewer.Type','Fuel.Type'))]

formulas <- map(vars, ~formula(paste0('Price ~ ',paste0(vars[vars != .x], collapse = '+'))))
names(formulas) <- paste0('full-Sewer.Type-Fuel.Type',vars)

homes_rm3varmodels <- workflow_set(preproc = formulas,models = list(lm = lm_spec))

homes_rm3varmodels_fit <- homes_rm3varmodels %>%
  workflow_map("fit_resamples", resamples = homes_cv10,  metrics = metric_set(rmse,rsq))

homes_rm3varmodels_fit %>% 
   rank_results() %>% 
   filter(.metric == "rmse") %>% 
   select(wflow_id, .config, rmse = mean, rank)
```

Removing AnyFireplaces gives the lowest error, meaning that removing it does the least harm to the predictive ability of the model. 

### Remove 4 from Model


```{r}
vars <- vars[!(vars %in% c('Price','Sewer.Type','Fuel.Type','AnyFireplace'))]

formulas <- map(vars, ~formula(paste0('Price ~ ',paste0(vars[vars != .x], collapse = '+'))))
names(formulas) <- paste0('full-Sewer.Type-Fuel.Type-AnyFireplace-',vars)

homes_rm4varmodels <- workflow_set(preproc = formulas,models = list(lm = lm_spec))

homes_rm4varmodels_fit <- homes_rm4varmodels %>%
  workflow_map("fit_resamples", resamples = homes_cv10,  metrics = metric_set(rmse,rsq))

homes_rm4varmodels_fit %>% 
   rank_results() %>% 
   filter(.metric == "rmse") %>% 
   select(wflow_id, .config, rmse = mean, rank)
```
Removing Fireplaces gives the lowest error, meaning that removing it does the least harm to the predictive ability of the model. 

### Remove 5 from Model


```{r}
vars <- vars[!(vars %in% c('Price','Sewer.Type','Fuel.Type','AnyFireplace','Fireplaces'))]

formulas <- map(vars, ~formula(paste0('Price ~ ',paste0(vars[vars != .x], collapse = '+'))))
names(formulas) <- paste0('full-Sewer.Type-Fuel.Type-AnyFireplace-Fireplaces-',vars)

homes_rm5varmodels <- workflow_set(preproc = formulas,models = list(lm = lm_spec))

homes_rm5varmodels_fit <- homes_rm5varmodels %>%
  workflow_map("fit_resamples", resamples = homes_cv10,  metrics = metric_set(rmse,rsq))

homes_rm5varmodels_fit %>% 
   rank_results() %>% 
   filter(.metric == "rmse") %>% 
   select(wflow_id, .config, rmse = mean, rank)
```

Removing Pct.College gives the lowest error, meaning that removing it does the least harm to the predictive ability of the model. 